---
title: "Introduction to this package"
author: "Li Feng"
date: "2023/12/8"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to this package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

This package implements two classic machine learning algorithms, PageRank and Kmeans. pageRank is a classic algorithm used to compute the ranking of Internet web pages, and this package provides the R function implementation of PageRank _pagerankr_, and the Rcpp implementation _pagerankc_, the following will use the R package 'microbenchmark' to compare the efficiency of the two implementations. Kmeans is a widely used clustering algorithm, this package provides its R function _kmeans_, we will try to call _kmeans_ in this package to perform clustering.

## PangeRank

To use the functions _pagerankr_ and _pagerankc_ provided in this package, an adjacency matrix must be provided. Here is an example of this simple adjacency matrix

```{r}
adj_matrix <- matrix(c(1, 0, 0, 0, 
                      0, 1, 0, 0, 
                      0, 0, 1, 0, 
                      1, 1, 1, 1), 
                    nrow = 4, byrow=TRUE)
```

Using the default arguments _alpha_ and _max_iter_ , you can get

```{r}
library(SA23229026)
pagerankr(adj_matrix)
pagerankc(adj_matrix)
```

The following uses 'microbenchmark' to compare efficiency

```{r}
library(microbenchmark)
ts <- microbenchmark(pagerankR=pagerankr(adj_matrix), pagerankc=pagerankc(adj_matrix))
summary(ts)[,c(1,3,5,6)]
```

As you can see, _pagerankc_ is much more efficient than _pagerankr_.

## Kmeans

Start by generating some random points

```{r}
set.seed(123)
data <- matrix(c(rnorm(30, 0, 0.2), rnorm(30, 2, 0.2), rnorm(30, 2, 0.2), 
                 rnorm(30, 0, 0.2), rnorm(30, 0, 0.2), rnorm(30, 2, 0.2)), ncol = 2)
plot(data)
```

Clustering using the _kmeans_ function in the package yields the following cluster centers and categories for each point

```{r}
result <- kmeans(data, 3)
result
```